---
title: "Curly Curly Guide"
author: "Stephanie"
date: "16/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, eval = FALSE)
```

Replacing quo, enquo and !! with {{. From the website https://edwinth.github.io/blog/dplyr-recipes/, I have tried to rewrite all of the examples using {{ instead, referencing https://www.tidyverse.org/blog/2019/06/rlang-0-4-0/.

```{r}
library(tidyverse)
```

## Bare to Quosure: quo

### Old:

```{r}
bare_to_quo <- function(x, var){
  x %>% select(!!var) %>% head(1)
}
bare_to_quo(mtcars, quo(cyl))

##           cyl
## Mazda RX4   6

```

### New:

{{ replaces both quo in the function call and !! in the function. Making this example the same as the following one.

```{r}
bare_to_quo <- function(x, var){
  x %>% select({{var}}) %>% head(1)
}
bare_to_quo(mtcars, cyl)

##           cyl
## Mazda RX4   6

```

## Bare to Quosure in Function: enquo

### Old:

```{r}
bare_to_quo_in_func <- function(x, var) {
  var_enq <- enquo(var)
  x %>% select(!!var_enq) %>% head(1)
}
bare_to_quo_in_func(mtcars, mpg)
##           mpg
## Mazda RX4  21

```

### New:

```{r}
bare_to_quo_in_func <- function(x, var) {
  x %>% select({{var}}) %>% head(1)
}
bare_to_quo_in_func(mtcars, mpg)
##           mpg
## Mazda RX4  21

```

## Quosure to a Name: quo_name

### Old:

```{r}
bare_to_name <- function(x, nm) {
  nm_name <- quo_name(nm)
  x %>% mutate(!!nm_name := 42) %>% head(1) %>% 
    select(!!nm)
}
bare_to_name(mtcars, quo(this_is_42))
##   this_is_42
## 1         42

```

### New:

```{r}
bare_to_name <- function(x, nm) {
  x %>% mutate({{nm}} := 42) %>% head(1) %>% 
    select({{nm}})
}
bare_to_name(mtcars, this_is_42)
##   this_is_42
## 1         42

```

## Quosure to Text: quo_text

### Old:

```{r}
quo_to_text <- function(x, var) {
  var_enq <- enquo(var)
  glue::glue("The following column was selected: {rlang::quo_text(var_enq)}")
}
quo_to_text(mtcars, cyl)

## The following column was selected: cyl

```

### New:

There is no replacement for this, as {{ does both enquo and !!, but only enquo is needed here. Another example is passing quo_to_text for the by argument of a join

## Quosure to Text: joins

### Old:

```{r}

tab1 <- tibble::tribble(
  ~A,  ~B,
   1, 500,
   2, 600,
   3, 700,
   4, 800
  )

tab2 <- tibble::tribble(
          ~A,       ~C,
           2, "Orange",
           1,   "Pink",
           4,  "Green",
           3,   "Blue"
          )

quo_to_text_joins <- function(x, y, var) {  
  var_enq <- enquo(var)
  temp <- left_join(x, y, by = rlang::quo_text(var_enq))
   }

quo_to_text_joins(tab1, tab2, A) %>% print()

##  A   B     C
##  1   500   Pink
##  2   600   Orange
##  3   700   Blue
##  4   800   Green

```

### New:

Again there is no replacement for this code using {{

## Character to Name: sym (edited)

### Old:

```{r}
char_to_quo <- function(x, var) {
  var_enq <- rlang::sym(var)
  x %>% select(!!var_enq) %>% head(1)
}
char_to_quo(mtcars, "vs")
##           vs
## Mazda RX4  0

```

### New:

This scenario uses the other half of enquo/!! duo. Only uses !! and hence no replacement for this code using {{. However, you can use the .data pronoun to simplify the code.

```{r}
char_to_quo <- function(x, var) {
  x %>% select(.data[[var]]) %>% head(1)
}
char_to_quo(mtcars, "vs")
##           vs
## Mazda RX4  0

```

## Multiple Bares to Quosure: quos

### Old:

```{r}
bare_to_quo_mult <- function(x, ...) {
  grouping <- quos(...)
  x %>% group_by(!!!grouping) %>% summarise(nr = n())
}
bare_to_quo_mult(mtcars, vs, cyl)
## # A tibble: 5 x 3
## # Groups:   vs [?]
##      vs   cyl    nr
##   <dbl> <dbl> <int>
## 1     0     4     1
## 2     0     6     3
## 3     0     8    14
## 4     1     4    10
## 5     1     6     4

```

### New:

Simply reference ..., no need for quos/!!! or {{. You only need quote-and-unquote (with the plural variants enquos() and !!!) when you need to modify the inputs or their names in some way.

```{r}
bare_to_quo_mult <- function(x, ...) {
  x %>% group_by(...) %>% summarise(nr = n())
}
bare_to_quo_mult(mtcars, vs, cyl)
## # A tibble: 5 x 3
## # Groups:   vs [?]
##      vs   cyl    nr
##   <dbl> <dbl> <int>
## 1     0     4     1
## 2     0     6     3
## 3     0     8    14
## 4     1     4    10
## 5     1     6     4

```

## Multiple Characters to Names: syms (edited)

### Old:

```{r}
bare_to_quo_mult_chars <- function(x, ...) {
  grouping <- rlang::syms(...)
  x %>% group_by(!!!grouping) %>% summarise(nr = n())
}
bare_to_quo_mult_chars(mtcars, list("vs", "cyl"))
## # A tibble: 5 x 3
## # Groups:   vs [?]
##      vs   cyl    nr
##   <dbl> <dbl> <int>
## 1     0     4     1
## 2     0     6     3
## 3     0     8    14
## 4     1     4    10
## 5     1     6     4

```

### New:

No replacement for this code, as it uses only half of enquo/!! syntax.

## Quoting Full Expression

Although quoting column names is most often used, it is by no means the only option. We can use the above to quote full expressions.

### Old:

```{r}
filter_func <- function(x, filter_exp) {
  filter_exp_enq <- enquo(filter_exp)
  x %>% filter(!!filter_exp_enq)
}
filter_func(mtcars, hp == 93)
##    mpg cyl disp hp drat   wt  qsec vs am gear carb
## 1 22.8   4  108 93 3.85 2.32 18.61  1  1    4    1

```

### New:

```{r}
filter_func <- function(x, filter_exp) {
  x %>% filter({{filter_exp}})
}
filter_func(mtcars, hp == 93)
##    mpg cyl disp hp drat   wt  qsec vs am gear carb
## 1 22.8   4  108 93 3.85 2.32 18.61  1  1    4    1

```

## Quoting Full Expression in a Character: parse_expr

### Old:

```{r}
filter_by_char <- function(x, char) {
  func_call <- rlang::parse_expr(char)
  x %>% filter(!!func_call)
}
filter_by_char(mtcars, "cyl == 6") %>% head(1)
##   mpg cyl disp  hp drat   wt  qsec vs am gear carb
## 1  21   6  160 110  3.9 2.62 16.46  0  1    4    4

```

### New:

No replacement for this code
